Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus in a Turkey B-cell Line

### 2024-03-21 manuscript_thev_transcriptome.Rmd
minor change in manuscript -- add a space conjoined words
Modified Rmd yaml to retain tex file for easy tracking of chages across versions

---
title: Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus in a Turkey B-cell Line
output:
  officedown::rdocx_document:
    reference_docx: style_word_output.docx
  pdf_document: default
geometry: margin=1in
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{placeins}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{caption}
  - \usepackage[labelformat=empty]{caption}
bibliography: transcriptome_refs.bib
csl: asm.csl
editor_options:
  chunck_output_type: console
---
\captionsetup[table]{labelformat=empty}

@@

![A flowchart of the major steps in the computationalanalysis pipeline (_generated with Snakemake_)](project_map.png)

>>>>

---
title: Characterizing the Transcriptome of Turkey Hemorrhagic Enteritis Virus in a Turkey B-cell Line
output:
  officedown::rdocx_document:
    reference_docx: style_word_output.docx
  pdf_document:
    keep_tex: true
geometry: margin=1in
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{placeins}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{caption}
  - \usepackage[labelformat=empty]{caption}
bibliography: transcriptome_refs.bib
csl: asm.csl
editor_options:
  chunck_output_type: console
---
\captionsetup[table]{labelformat=empty}

@@

![A flowchart of the major steps in the computational analysis pipeline (_generated with Snakemake_)](project_map.png)
